Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2014-12-04 fib2.tex
cleaned up line breaks and some references.

\begin{abstract}
Simulating the dynamics of excitations in two-dimensional quantum systems that support 
anyons is intractable in general because it is sufficient for universal quantum computation. 
Here we show that for typical processes of interest for the study of quantum error correction 
in anyon systems, the relevant dynamics can in fact be efficiently simulated classically for a 
wide range of system parameters, even when the underlying anyon model is universal. We 
make use of this fact to demonstrate the success of an error-correction protocol for a 
Fibonacci anyon quantum memory. We numerically simulate a phenomenological model of 
the system and noise processes on lattice sizes of up to $128\times128$ sites, and 
demonstrate an error-correction threshold of around $12.5\%$, a number that is comparable 
to those previously known for abelian and (non-universal) non-abelian anyon models.
\end{abstract}

@@

Here we consider a full simulation of quantum error correction in a two-dimensional lattice system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum computation~\cite{Wang2010b}. \stf{Describe main results and why they are bad ass.}

>>>>

\begin{abstract}
Simulating the dynamics of excitations in two-dimensional quantum systems that support 
anyons is intractable in general because it is sufficient for universal quantum computation. 
Here we show that for typical processes of interest for the study of quantum error correction 
in anyon systems, the relevant dynamics can in fact be efficiently simulated classically for a 
wide range of system parameters, even when the underlying anyon model is universal. We 
make use of this fact to demonstrate the success of an error-correction protocol for a 
Fibonacci anyon quantum memory. We numerically simulate a phenomenological model of 
the system and noise processes on lattice sizes of up to $128\times128$ sites, and 
demonstrate an error-correction threshold of around $12.5\%$, a number that is comparable 
to those previously known for abelian and (non-universal) nonabelian anyon models.
\end{abstract}

@@

Here we consider a full simulation of quantum error correction in a two-dimensional lattice 
system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
computation~\cite{Wang2010b}. Fibonacci anyons are experimentally motivated as the 
expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
states~\cite{Slingerland2001}, and can also be realized in several spin 
models~\cite{Levin2005, Kapit2013, Palumbo2014}. 
\stf{Describe main results and why they are bad ass.}
